Appendix: Stop Lying to Me: New Visual Tools to Choose the Most Honest Nonlinear Dimension Reduction

### 2025-06-26 appendix.qmd
Updated appendix Figure 1

two_curvy_proj_true1 <- plot_proj(
  proj_obj = proj_obj1_true,
  point_param = c(0.5, 0.2, clr_choice), # size, alpha, color
  line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha
  plot_limits = c(-0.75, 0.75),
  axis_text_size = 2,
  is_category = FALSE) +
  interior_annotation(label = "a", cex = 1.2) +
  theme(aspect.ratio = 1,
        legend.position = "none")

@@

two_curvy_proj_true2 <- plot_proj(
  proj_obj = proj_obj2_true,
  point_param = c(0.1, 0.5, clr_choice), # size, alpha, color
  line_param = c(0.5, 0.5, "black"), # linewidth, alpha
  plot_limits = c(-0.5, 0.5),
  axis_text_size = 2,
  is_category = FALSE) +
  interior_annotation(label = "b", cex = 1.2) +
  theme(aspect.ratio = 1)
```

```{r}
#| fig-width: 6
#| fig-height: 3
#| fig-cap: "Two projections of the \\pD{} true model overlaying the data are shown in a, b."

two_curvy_proj_true1 + two_curvy_proj_true2
```

>>>>

two_curvy_proj_true1 <- plot_proj(
  proj_obj = proj_obj1_true,
  point_param = c(0.5, 0.2, clr_choice), # size, alpha, color
  line_param = c(0.5, 0.3, "#000000"), # linewidth, alpha
  plot_limits = c(-0.75, 0.75),
  axis_text_size = 4,
  is_category = FALSE) +
  interior_annotation(label = "a", cex = 2) +
  theme(aspect.ratio = 1,
        legend.position = "none")

@@

two_curvy_proj_true2 <- plot_proj(
  proj_obj = proj_obj2_true,
  point_param = c(0.1, 0.5, clr_choice), # size, alpha, color
  line_param = c(0.5, 0.3, "black"), # linewidth, alpha
  plot_limits = c(-0.5, 0.5),
  axis_text_size = 4,
  is_category = FALSE) +
  interior_annotation(label = "b", cex = 2) +
  theme(aspect.ratio = 1)
```

```{r}
#| fig-width: 10
#| fig-height: 5
#| fig-cap: "Two projections of the \\pD{} true model overlaying the data are shown in a, b."

two_curvy_proj_true1 + two_curvy_proj_true2 +
  plot_layout(ncol = 2)
```
